LAGOS lake depth

### 2019-09-24 lagos_depth.Rmd
add area and conny class

```{r setup, include=FALSE}
# https://stackoverflow.com/a/24600461/3362993
knitr::knit_hooks$set(timeit = local({
  now = NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res = difftime(Sys.time(), now)
      now <<- NULL
      # use options$label if you want the chunk label as well
      paste('Time for this code chunk:', as.character(round(res, 2)))
    }
  }})
)

knitr::opts_chunk$set(echo = FALSE, timeit = TRUE, eval = FALSE)
source("scripts/99_utils.R")
```

```{r data, message=FALSE, echo=FALSE, eval=TRUE}
dt <- read.csv("data/lagosus_depth.csv", stringsAsFactors = FALSE) %>%
  mutate(maxdepth_class = cut(max_depth_m, 
                     round(quantile(max_depth_m, c(0, 0.05, 0.5, 0.95, 1), 
                                    na.rm = TRUE)))) %>% 
  coordinatize(latname = "lat", longname = "long")
```

>>>>

```{r timings, include=FALSE}
# https://stackoverflow.com/a/24600461/3362993
knitr::knit_hooks$set(timeit = local({
  now = NULL
  function(before, options) {
    if (before) {
      now <<- Sys.time()
    } else {
      res = difftime(Sys.time(), now)
      now <<- NULL
      # use options$label if you want the chunk label as well
      paste('Time for this code chunk:', as.character(round(res, 2)))
    }
  }})
)
```

```{r setup, include=FALSE}
source("scripts/99_utils.R")
knitr::opts_chunk$set(echo = FALSE, timeit = TRUE, eval = FALSE)
```

```{r data, message=FALSE, echo=FALSE, eval=TRUE}
dt <- read.csv("data/lagosus_depth.csv", stringsAsFactors = FALSE) %>%
  mutate(maxdepth_class = cut(max_depth_m, 
                     round(quantile(max_depth_m, c(0, 0.05, 0.5, 0.95, 1), 
                                    na.rm = TRUE)))) %>% 
  # TODO: join with locus preview
  coordinatize(latname = "lat", longname = "long")
```
